Community context determines competition/facilitation trade-offs in pollination systems

### 2019-04-26 paper/manuscript.Rmd
Add keywords
Remove ref to supp info figure that has been removed too

**Keywords:** X,Y,Z (up to 10).

@@

To investigate the impact of ecological factors on pollination service we used two sets of linear mixed models (LMM) with bootstrap resampling.
The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
We used LMMs in which pollen loads were log-transformed (Figure \@ref(S-fig:fig-deposition-gain-log-transformed-or-not)) because these models offered a better fit than a GLMM with Poisson (or quasipoisson) error structure. 
Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].

>>>>

**Keywords:** Competition, facilitation, interspecific pollen transfer, conspecific, pollen deposition, multi-species, plant-pollinator interaction, pollination trade-off, pollination costs, networks (up to 10).

@@

To investigate the impact of ecological factors on pollination service we used two sets of linear mixed models (LMM) with bootstrap resampling.
The response variables for these model sets were the number of conspecific and heterospecific pollen grains deposited per stigma in flowers open to animal-mediated pollination. 
We used LMMs in which pollen loads were log-transformed because these models offered a better fit than a GLMM with Poisson (or quasipoisson) error structure. 
Models were fitted using the R package `nlme 3.1-131` [@pinheiro_nlme_2018].
